\usefont{OT1}{bch}{b}{n} \normalfont \normalsize \textsc{School of random department names} \\ [25pt] \horrule{0.5pt} \\[0.4cm] \huge This is the title of the template report \\ \horrule{2pt} \\[0.5cm]

### 2018-05-25 Report/notes.tex
renaming picture

		const int k = 10;
		const int qCapacity = 10;

		const double timeout = 10;
		const double lambda = 0.2;

@@

		[] i < k -> k/timeout : (i'=i+1);
		[produce] i = k -> k/timeout : (i'=1);
		//[consume] true -> (i'=1);

		\end{lstlisting}
		\caption{PRISM CTMC model of the D/M/1/n queue as shown in \ref{fig:Queue1} with phase-type fitting to approximate the deterministic arrivals. The phase-type module \emph{trigger} is used as suggested on the \href{http://www.prismmodelchecker.org/manual/FrequentlyAskedQuestions/PRISMModelling}{PRISM website}.  }
		\label{fig:queuecode2}
	\end{figure}

@@

	\begin{figure}
		\centering
		\includegraphics[width=16cm]{picture/time.png}
		\caption{Computation time for different values of $k$. The growing lines represent computations of models with phase-type distributions. For about $k>200$, GSMP implementation starts outperforming all phase-typed computations, despite the GSMP implementation being relatively poorly optimized.}
		\label{fig:time1}
	\end{figure}

	\begin{figure}
		\centering
		\includegraphics[width=16cm]{picture/size.png}
		\caption{Size of model for different values of $k$.}
		\label{fig:time1}
	\end{figure}

@@

	\begin{figure}
		\centering
		\includegraphics[width=18cm]{picture/dist02_explicit_01.png}
		\caption{Euclidean Distance of distribution of the SSP computation between the event model and the PTF model using explicit engine versus the PTF parameter k,	$t=0.1$,$\lambda=1/t$,$\epsilon=10^{-5}$}
		\label{fig:dist02_explicit_001}
	\end{figure}

>>>>

const int k;
const int qCapacity = 10;

const double timeout;
const double lambda;

@@

[] i < k & qSize<qCapacity -> k/timeout : (i'=i+1);
[produce] i = k -> k/timeout : (i'=1);

endmodule
		\end{lstlisting}
		\caption{PRISM CTMC model of the D/M/1/n queue as shown in \ref{fig:Queue1} with phase-type fitting to approximate the deterministic arrivals. The phase-type module \emph{trigger} is used as suggested on the \href{http://www.prismmodelchecker.org/manual/FrequentlyAskedQuestions/PRISMModelling}{PRISM website}.  }
		\label{fig:queuecode2}
	\end{figure}

@@

	\begin{figure}
		\centering
		\includegraphics[width=16cm]{picture/time_of_computation.png}
		\caption{Computation time for different values of $k$. The growing lines represent computations of models with phase-type distributions. For about $k>200$, GSMP implementation starts outperforming all phase-typed computations, despite the GSMP implementation being relatively poorly optimized.}
		\label{fig:time1}
	\end{figure}

	\begin{figure}
		\centering
		\includegraphics[width=16cm]{picture/size.png}
		\caption{Size of model for different values of $k$. $\#\{$state$\} = nk+1$}
		\label{fig:time1}
	\end{figure}

@@

	\begin{figure}
		\centering
		\includegraphics[width=18cm]{picture/eucl_distance.png}
		\caption{Euclidean Distance of distribution of the SSP computation between the event model and the PTF model using explicit engine versus the PTF parameter k,	$t=0.1$,$\lambda=1/t$,$\epsilon=10^{-5}$}
		\label{fig:dist02_explicit_001}
	\end{figure}
